%-------------------------
% Resume in Latex
% Author : Nishant Khandhar
% License : MIT
%------------------------

\documentclass[letterpaper, 15pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-.65in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-9pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-3pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}


%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Nishant Khandhar} \\ \vspace{2pt}
    \small XXX-XXX-XXXX $|$ \href{mailto:your_mail_address}{\underline{abc@xyz.com}} $|$ 
    \href{https://linkedin.com/in/nishant-khandhar}{\underline{linkedin.com/in/nishant-khandhar}} $|$
    \href{https://github.com/nishant-k02}{\underline{github.com/nishant-k02}}
\end{center}

%-----------TECHNICAL SKILLS-----------

\section{Technical Skills} 
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Dart, Java, C++, JavaScript} \\
     \textbf{Frontend and Frameworks}{: ReactJS, Flutter, HTML, CSS, Bootstrap, JSP, Servlet, Full Stack development, Web Development.} \\
     \textbf{Backend}{: NodeJS, ExpressJS, Django, Flask, PHP, Firebase} \\
     \textbf{Database}{: SQL, MySQL, PostgreSQL, SQlite3, MongoDB, NoSQL, ElasticSearch} \\
     \textbf{Developer Tools}{: Github, Visual Studio, Atom, PyCharm, IntelliJ, Eclipse, Android Studio, Jupyter Notebook, Postman} \\
     \textbf{Libraries}{: Pandas, NumPy, Matplotlib, OpenCV, TensorFlow, sklearn, os, autogen, openAI}
    }}
 \end{itemize}


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Developer Intern - Android Developer}{Feb 2023 -- Mar 2023}
      {Visanka Technologies}{Chennai, India}
      \resumeItemListStart
        \resumeItem{Developed an \textbf{Android-based (JAVA)} Job Portal App simplifying job searches for seekers, while assisting employers in managing applications and optimizing the hiring process.}
        \resumeItem{Developed features like Job Applications, Management, and User Authentication.}
        \resumeItem{\textbf{Tech Stack:} Java, MySQL, XMAPP, Firebase, PHP, Android Studio, Github} \vspace{5pt}
      \resumeItemListEnd
      
    \resumeSubheading
      {Software Developer Intern - Web Developer}{Jun 2021 -- Aug 2021}
      {The Sparks Foundation}{Pune, India}
      \resumeItemListStart
        \resumeItem{Developed an online banking system using \textbf{Flask} that enables account-to-account money transfer and keeps detailed transaction records to improve financial monitoring.}
        \resumeItem{\textbf{Tech Stack:} Python, Flask, SQlite3, Pycharm, HTML, CSS}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

   \resumeProjectHeading
      {\textbf{Health Care AI Assistant}}{Sept 2024 -- Nov 2024}
      \resumeItemListStart
        \resumeItem{Developed an AI-powered healthcare assistant that enables users to describe symptoms and receive personalized medical suggestions  \textbf{using OpenAI's LLM through AutoGen} that analyses symptoms, retrieve relevant medicines, and provide a non-panic-inducing summary.}
        \resumeItem{Integrated a Conversational User Bot to guide customers to classify order statuses (Refund, Return, or Escalate to Human) with 90\% accuracy, leveraging order IDs, payment details.}
        \resumeItem{Implemented \textbf{GPT-based decision-making logic} using OCR-processed receipts to automate the detection of fraudulent transactions with 70\% accuracy, enabling precise classifications like Refund, Decline, or Escalate.}
        \resumeItem{\textbf{Tech Stack:}  Flutter, Dart, FastAPI, Uvicorn, AutoGen, Open AI, XML, Python, RESTful API, PostgreSQL, Chroma DB, Python, MongoDB, Flask.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Car Damage Detection}}{Aug 2023 -- Mar 2024}
      \resumeItemListStart
        \resumeItem{Developed an end-to-end web app leveraging \textbf{Computer Vision} for precise vehicle damage detection and assessment with 90\% accuracy.}
        \resumeItem{Trained a \textbf{Convolutional Neural Network (CNN)} on annotated vehicle images to predict damage severity.}
        \resumeItem{\textbf{Tech Stack:} Python, Pandas, Django, OpenCV, TensorFlow, Keras, Jupyter Notebook, HTML, CSS.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Covid Statistics Analyzer}}{Apr 2021 -- Jul 2021}
      \resumeItemListStart
        \resumeItem{Created a \textbf{Power BI dashboard} to visualize live COVID-19 metrics country-wise, state-wise, and city-wise.}
        \resumeItem{Integrated APIs to gather and parse data using Python, enhancing data accuracy by 50\%.}
        \resumeItem{Visualized key features such as recovery rate, mortality rate, and critical case statistics for over 1,000 stakeholders.}
        \resumeItem{\textbf{Tech Stack:} Python, Power BI, API Integration.}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Online Code Editor}}{Jul 2024 -- Aug 2024}
      \resumeItemListStart
        \resumeItem{Designed a responsive, user-friendly online code editor for real-time code writing, editing, and previewing.}
        \resumeItem{Enabled seamless cross-device functionality with features like syntax highlighting and live preview.}
        \resumeItem{\textbf{Tech Stack:} React, Bootstrap, CodeMirror, JavaScript, HTML, CSS.}
      \resumeItemListEnd

  % \resumeSubHeadingListEnd


    % \resumeProjectHeading
    %   {\textbf{Android Weather App}}{Apr 2022 -- May 2022}
    %   \resumeItemListStart
    %     \resumeItem{Developed an Android application to provide real-time climate updates using \textbf{Weather API} based on user-input locations, delivering accurate weather data to over 500 users.}
    %     \resumeItem{Integrated features such as temperature, humidity, wind speed, sunrise, and sunset time, improving user experience by 35\% through intuitive data presentation and on-demand weather insights.}
    %     \resumeItem{\textbf{Tech Stack:} Java, Android Studio, Weather API (that enhanced application efficiency by 40\%)}
    %   \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Illinois Institute of Technology }{Chicago, IL}
      {Master of Computer Science |\textbf{ GPA: 4.00}}{May 2026}
        \resumeItemListStart
          \resumeItem{Top Courses: Enterprise Web Application, Machine Learning, Software Systems Architecture, Software Modeling Development using UML, Mobile Application Development}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------RESEARCH PUBLICATION-----------
\section{Research Publications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \item \textbf{\href{https://www.jetir.org/view?paper=JETIR2311193}{Car Damage Detection Using Computer Vision}} 
    \newline Journal of Emerging Technologies and Innovative Research (JETIR), Volume 10, Issue 11, 2023.
\end{itemize}

%-----------COMMUNITY AND LEADERSHIP-----------
\section{Community \& Leadership}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Android Developer Lead}{2022 -- 2023}
      {Google Developer Student Clubs (GDSC)}{Pune, India}
      \resumeItemListStart
        \resumeItem{Led a team of 50 students in creating innovative mobile applications. Organized and conducted seminars on Android development best practices and emerging technologies.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
